

```{r}
---
#Article title: R Markdown for "A unique 75 000 year old Arctic faunal community preserved in a cave in northern Fennoscandia"
#Section: "Building a blast table"
#Author of this script: "Aurélie Boilard"
#Institutional email : "aurelibo@uio.no"
#Personal email : "aurelie.boilard.1@outlook.com"
#Updated : "June 2024"
---

```{r}


#Activate the following R packages
library(tidyverse)
library(dplyr)
library(ggplot2)

#Use readr to import dataset
#Filter to keep only what has over 95% for Fish16S and Aves12S. For Mamp007, identity for mammalian taxa need to be above 98% and 95% for birds and fish picked up by this primer. The easiest way to do so is to generate two tables for Mamp007 (one 95% and one 98%) and respectively use the 98% to look up the mammal sequences and the 95% to search for birds and fish.

#This markdown is an example for the Aves12S primer.
taxo_2021 <- NO2021taxo_005_bird_Nov2023
taxo_2022 <- NO2022taxo_005_bird_Nov2023

taxo_raw_2021 <- taxo_2021[taxo_2021$`best_identity:birds_feb2022` > 0.95,]
taxo_raw_2022 <- taxo_2022[taxo_2022$`best_identity:birds_feb2022` > 0.95,]

taxo_final_2021 <- taxo_raw_2021[,c("id","best_identity:birds_feb2022","count", "scientific_name", "species_list:birds_feb2022", "species_name", "taxid", "sequence")]

taxo_final_2022 <- taxo_raw_2022[,c("id","best_identity:birds_feb2022","count", "scientific_name", "species_list:birds_feb2022", "species_name", "taxid", "sequence")]

taxo_all <- rbind(taxo_final_2021, taxo_final_2022) 

write_csv(taxo_all, "/Users/aurelibo/Desktop/PhD/Projet/EvoCave/Papers/Arne_Qvam/GitHub/Makeblast_table/NOAves12S_95_blast_2024.csv")

#You can either combine all tables in one Excel file using different sheets or use each table separately.


